Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-16 numerical-mhd-ct.tex
fixing some references.

Dual energy formalism has also been incorporated in two methods, one internal
energy, similar to that described in Section \ref{sec.hydro.ppm}, and one that
uses entropy.  The additional equations are
\begin{eqnarray}
\end{eqnarray}
\begin{eqnarray}
  \frac{\partial S}{\partial t} +\frac{1}{a} \nabla \cdot (S \vecv) & = &  -
  \frac{ 3 (\gamma - 1) \dot{a}}{a} S \\
  \frac{\partial \rho e}{\partial t} + \frac{1}{a} \nabla \cdot (\rho e \vecv) &
  = & -\frac{ 3(\gamma -1 ) \dot{a}}{a} + \frac{p}{a} \nabla \cdot \vecv,
\end{eqnarray}
where $e$ is the internal energy and $S=p/\rho^{\gamma-1}$ is the entropy.  If
the ratio of thermal to kinetic energy, $\eta$, is below a certain value, the
alternative energy is used.  As in \citet{Li08}, we use $\eta=0.008$.

Enzo's MHD-CT has been used in a variety of contexts, from galaxy
cluster evolution \citep{Xu11,Xu12}, synthetic observations of radio
halos \citep{Skillman13}, primordial star formation \citep{Xu08}, and
present-day star formation \citep{Collins11,Collins12}.

>>>>

Dual energy formalism has also been incorporated in two methods, one internal
energy, similar to that described in Section \ref{sec.hydro.ppm}, and one that
uses entropy.  The additional equations are
\begin{eqnarray}
\end{eqnarray}
\begin{eqnarray}
  \frac{\partial S}{\partial t} +\frac{1}{a} \nabla \cdot (S \vecv) & = &  -
  \frac{ 3 (\gamma - 1) \dot{a}}{a} S \\
  \frac{\partial \rho e}{\partial t} + \frac{1}{a} \nabla \cdot (\rho e \vecv) &
  = & -\frac{ 3(\gamma -1 ) \dot{a}}{a} + \frac{p}{a} \nabla \cdot \vecv,
\end{eqnarray}
where $e$ is the internal energy and $S=p/\rho^{\gamma-1}$ is the entropy.  If
the ratio of thermal to kinetic energy, $\eta$, is below a certain value, the
alternative energy is used.  As in \citet{Li08a}, we use $\eta=0.008$.

Enzo's MHD-CT has been used in a variety of contexts, from galaxy
cluster evolution \citep{Xu11,Xu12}, synthetic observations of radio
halos \citep{Skillman13}, primordial star formation \citep{Xu08}, and
present-day star formation \citep{Collins11, Collins12a}.
